A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-08 4_method.tex
rename sections;  section -> subsection etc.

\subsection{Significance measure}\label{sec:significance_measure}
\Cref{rounded_dist_measures}
We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
Equivalently we can look at the \emph{bisector angle} $\alpha$ between a skeletal point and the two closest points on the outline.
(Same definition as \cite{attali1996modeling}.)

@@

\subsubsection{MAT distance transform}
In order to apply the beading strategy to the MAT
we assign each node $v$ of the medial axis a bead quantity $B^*$ which is initially based on $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.

@@

\subsection{Transitioning}

@@

\subsection{Tick placement}
\hl{Change terminology: location $\to$ junction?}

@@

\subsection{Spacing problems}
Applying a beading strategy to the skeleton might not be trivial.
The trivial approach explained above introduces slight deviations from the beading strategy at intermediate locations in a quad.
When the widths are always the same this doesn't happen, but with widths changing throughout a quad this can pose a slight problem.

@@

\subsection{Toolpath extraction}
\paragraph{Processing order}
\hl{How do we process the graph?}
\begin{itemize}
\item walk along polygons and for each vert walk down the graph up to the desired depth
\item process nodes in depth first order
\item process nodes in $R$ sorted order
\end{itemize}

>>>>

\subsection{Beading}
We assign a beading to each significant node (and each local optimum).

\subsubsection{Significance measure}\label{sec:significance_measure}
\Cref{rounded_dist_measures}
We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
Equivalently we can look at the \emph{bisector angle} $\alpha$ between a skeletal point and the two closest points on the outline.
(Same definition as \cite{attali1996modeling}.)

Contrary to common techniques we will \emph{keep} the insignificant regions of the skeleton.

@@

\paragraph{MAT distance transform}
In order to apply the beading strategy to the MAT
we assign each node $v$ of the medial axis a bead quantity $B^*$ which is initially based on $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.

@@

\subsubsection{Transitioning}

@@

\subsection{Toolpath extraction}

\subsubsection{Tick placement}
\hl{Change terminology: location $\to$ junction?}

@@

\subsubsection{Spacing problems}
Applying a beading strategy to the skeleton might not be trivial.
The trivial approach explained above introduces slight deviations from the beading strategy at intermediate locations in a quad.
When the widths are always the same this doesn't happen, but with widths changing throughout a quad this can pose a slight problem.

@@

\subsubsection{Processing order}
\hl{How do we process the graph?}
\begin{itemize}
\item walk along polygons and for each vert walk down the graph up to the desired depth
\item process nodes in depth first order
\item process nodes in $R$ sorted order
\end{itemize}
